Non-word repetition in Yélî Dnye

### 2020-09-07 manuscript.Rmd
minor

## TODO later
- probably turn summary of types of error into a table; use proportion of correctly produced rather than number; use first attempts rather than the whole data set
- maybe add to the last ana the prevalence (ie out of all the gh which proportion get transformed)
- maybe add analyses of score as a function of frequency (phones, diphones) in MC's corpus? (mc suggested, but I don't think we need it...)

@@

We visited four different hamlets once, and attempted to test all eligible children present at the time, to prevent the items 'spreading' through hearsay. In the first hamlet, we tested children in five different places, with some children being tested inside a house and others tested on the veranda. The complete list of places and the ways in which they met the desiderata mentioned above can be found in the raw data, available from online supplementary materials.
 <!--M2A: I didn't look for the SM yet, but probably best not to provide exact hamlet names-->

>>>>

## TODO later
- probably turn summary of types of error into a table; use proportion of correctly produced rather than number; use first attempts rather than the whole data set DONE
- maybe add to the last ana the prevalence (ie out of all the gh which proportion get transformed) DONE I think... (this item looks the same as one of the three above)
- maybe add analyses of score as a function of frequency (phones, diphones) in MC's corpus? (mc suggested, but I don't think we need it...) - waiting until we talk about this

@@

We visited four different hamlets once, and attempted to test all eligible children present at the time, to prevent the items 'spreading' through hearsay. In the first hamlet, we tested children in five different places, with some children being tested inside a house and others tested on the veranda. The complete list of places and the ways in which they met the desiderata mentioned above can be found in the raw data, available from online supplementary materials.
 <!--M2A: I didn't look for the SM yet, but probably best not to provide exact hamlet names-->
<!--a2m: good point! fixed-->
